GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations

### 2024-12-29 writeUps/paper.tex
update2

\begin{figure}
  \centering
  \includegraphics{prinEffs.pdf}
  \caption{Principal effect estimates with 95\% confidence intervals using three different principal score models, alongside ATE estimates and 95\% confidence intervals, for contrasts between the ASSISTments condition and each of the three other conditions in the study.}
  \label{fig:effects}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{compareMethods.pdf}
  \caption{Principal effect estimates with 95\% confidence or credible intervals using three different principal stratification methods, alongside ATE estimates and 95\% confidence intervals, for contrasts between the ASSISTments condition and each of the three other conditions in the study. The \textsc{geepers} estimates used the ``All Covariates'' principal score model.}
  \label{fig:compare}
\end{figure}

@@

\begin{center}
    \includegraphics[width=5.5in]{simFigs/alphaAUC.pdf}
\end{center}
%\begin{table}
%\caption{Coverage of nominal 95\% confidence intervals}
\clearpage

\subsection{Full Empirical 95\% Interval Coverage Results}
The following table gives the empirical coverage of nominal 95\% intervals for \textsc{geepers} and mixture model principal effect estimates under varying data generating models.\\
\input{writeUps/coverageTabAppendix.tex}

\clearpage
\subsection{Full RMSE Results}
The following table gives the root mean squared error (RMSE) for \textsc{geepers}, mixture model, and principal score weighting principal effect estimates under varying data generating models.\\
\input{writeUps/rmseTabAppendix}

@@

\section{Additional Results from the Application}
\singlespacing
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

\subsection{Summary Statistics}
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\
\small
\input{tab1fac}
\clearpage

\small
\input{writeUps/tab1num}

\subsection{Regression Results}
Regression estimates from three principal score logit models and three outcome regressions, based on the "All Covariates" principal score model, for \textsc{geepers} estimates. Standard errors shown are nominal regression errors, not sandwich corrected. Fixed-effect estimates for school (PS-models) or classroom (outcome models) are omitted.

\small
%\input{writeUps/outcomeRegAppendix}
\input{writeUps/psTab}

\input{writeUps/regTab}

>>>>

\begin{figure}
  \centering
  \includegraphics{figure/prinEffs.pdf}
  \caption{Principal effect estimates with 95\% confidence intervals using three different principal score models, alongside ATE estimates and 95\% confidence intervals, for contrasts between the ASSISTments condition and each of the three other conditions in the study.}
  \label{fig:effects}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{figure/compareMethods.pdf}
  \caption{Principal effect estimates with 95\% confidence or credible intervals using three different principal stratification methods, alongside ATE estimates and 95\% confidence intervals, for contrasts between the ASSISTments condition and each of the three other conditions in the study. The \textsc{geepers} estimates used the ``All Covariates'' principal score model.}
  \label{fig:compare}
\end{figure}

@@

\begin{center}
    \includegraphics[width=5.5in]{../simFigs/alphaAUC.pdf}
\end{center}
%\begin{table}
%\caption{Coverage of nominal 95\% confidence intervals}
\clearpage

\subsection{Full Empirical 95\% Interval Coverage Results}
The following table gives the empirical coverage of nominal 95\% intervals for \textsc{geepers} and mixture model principal effect estimates under varying data generating models.\\
\input{coverageTabAppendix.tex}

\clearpage
\subsection{Full RMSE Results}
The following table gives the root mean squared error (RMSE) for \textsc{geepers}, mixture model, and principal score weighting principal effect estimates under varying data generating models.\\
\input{rmseTabAppendix}

@@

% \section{Additional Results from the Application}
% \singlespacing
% The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

% \subsection{Summary Statistics}
% The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\
% \small
% \input{tab1fac}
% \clearpage

% \small
% \input{tab1num}

% \subsection{Regression Results}
% Regression estimates from three principal score logit models and three outcome regressions, based on the "All Covariates" principal score model, for \textsc{geepers} estimates. Standard errors shown are nominal regression errors, not sandwich corrected. Fixed-effect estimates for school (PS-models) or classroom (outcome models) are omitted.

% \small
% %\input{writeUps/outcomeRegAppendix}
% \input{psTab}

% \input{regTab}
